\section{Datasets}
The report evaluates the same predictive-maintenance formulation across four local dataset families. Together they cover simulated engine degradation, laboratory run-to-failure bearings, seeded machinery faults, and building HVAC faults. That breadth matters because a looped reasoning model is only useful if it can preserve its advantage when the sensing modality and failure process change.

\subsection{C-MAPSS}
The C-MAPSS turbofan simulation data provide multivariate time series recorded under multiple operating conditions and fault modes \cite{Saxena2008CMAPSS}. Each trajectory follows an engine from healthy operation to failure, making it suitable for supervised prognostics. The dataset is widely used in prognostic benchmarking because it supports several failure prediction formulations, including direct RUL regression and classification via thresholded remaining life \cite{Ramasso2014CMAPSS}.

The training protocol uses rolling windows of sensor data and derives labels from remaining useful life thresholds to produce ``normal,'' ``warning,'' and ``critical'' classes. Windows use length 32 and stride 8. Thresholds are set to RUL $> 50$ for normal, $15 < \text{RUL} \leq 50$ for warning, and $\text{RUL} \leq 15$ for critical.

\subsection{IMS Bearings}
The IMS bearing dataset contains high-frequency vibration snapshots from run-to-failure experiments on rotating bearings \cite{NASAIMSBearings}. The data are stored as timestamped ASCII files and do not ship with explicit health labels, so labels must be derived from time ordering and the failure endpoint. This makes IMS useful for anomaly detection, degradation staging, and transfer testing.

\subsection{LBNL Fan-Coil HVAC Faults}
The LBNL fan-coil unit fault dataset contains labeled building-equipment trajectories covering fault-free operation, airflow restrictions, damper faults, valve leakage and sticking, fouling, control reversal, and sensor bias conditions \cite{LBNLFDD2023}. In this project, each CSV file is treated as one equipment episode, filename tokens are mapped into health, maintenance-action, and subsystem targets, and minute-level readings are downsampled before rolling windows are formed. This dataset is useful because it tests the same maintenance-triage framing on building systems rather than engines or bearings.

\subsection{Paderborn Bearings}
The Paderborn bearing data center contains healthy bearings together with seeded and real bearing damage states recorded under several operating conditions \cite{PaderbornBearingDataset}. The archive is distributed as MATLAB files, so the implementation reads vibration, current, force, speed, and torque channels directly from the zip file, aligns them to a common sample length, and then applies rolling windows. Healthy bearings are mapped to the normal class, artificial damage states to warning, and real damage states to critical. This benchmark is not run-to-failure; instead it acts as a state-classification extension that checks whether the looped model still beats text-serialized LLM baselines on machinery data.

\subsection{Benchmark Matrix}
\begin{table}[t]
\centering
\caption{Datasets used in OuroMaintain}
\label{tab:datasets}
\begin{tabular}{@{}p{1.8cm}p{1.8cm}p{1.7cm}p{2.4cm}@{}}
\toprule
Dataset & Modality & Supervision & Primary use \\
\midrule
C-MAPSS & Engine telemetry & RUL thresholding & Main supervised benchmark \\
IMS bearings & Vibration snapshots & Derived from failure order & Run-to-failure check \\
LBNL FCU & HVAC telemetry & Fault-file labels & Building-system extension \\
Paderborn & Bearing measurements & Bearing-state labels & Machinery extension \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Preprocessing}
The implemented preprocessing pipeline standardizes sensor channels using statistics fit on the training split, generates overlapping windows, and aligns labels to each window end point. Validation splits are created at the engine level for C-MAPSS to avoid leakage between windows from the same asset. For IMS, the pipeline converts each vibration snapshot into summary statistics per channel and then applies temporal windows over the derived feature stream. For HVAC and Paderborn, the validation split is asset-label stratified so that each validation fold contains normal, warning, and critical states without mixing windows from the same equipment episode or bearing measurement.

\subsection{How the Datasets Are Used}
Not every dataset supports the exact same comparison. C-MAPSS provides official train/test splits and is therefore used for the full model comparison plus latency and depth analysis. IMS uses validation-only reporting because its labels are derived from failure progression and the current protocol does not expose a separate official test split. Paderborn is used as the matched cross-domain machinery comparison because all three model families completed there. LBNL HVAC is used as a cross-domain transfer benchmark for the looped model under stricter asset-level splits.
