\section{Deployment Considerations}
Although the current project is a research system, predictive maintenance is ultimately a workflow problem. The implementation now includes a lightweight Streamlit dashboard that reads experiment artifacts, visualizes model comparisons, and lets a user inspect benchmark windows through the trained adaptive model. The dashboard returns a health state, class confidence, and adaptive depth trace for the selected example. That output gives operators a concise summary while still exposing how much internal computation was needed.

\subsection{Operational Flow}
In a live setting, the system would ingest sensor batches on a fixed cadence, convert them into sliding windows, and score each asset independently. If the model repeatedly returns warning or critical states across several windows, the decision policy should escalate to a human operator or a maintenance ticketing system. The early-exit depth can be logged as a diagnostic signal that helps distinguish easy high-confidence cases from ambiguous cases that deserve manual inspection. The current dashboard mirrors that flow at demo scale by combining benchmark metrics, model-history plots, confusion matrices, and per-window inference traces in one interface.

\subsection{Reproducibility}
The final report should document the exact dataset version, preprocessing parameters, random seeds, and train/validation/test split definitions. That matters especially for IMS, where label construction is derived and therefore sensitive to the chosen failure horizon. A reproducible scaffold should also record software versions and the command used to train each model variant.

\subsection{Practical Limitations}
There are two main limitations to acknowledge. First, thresholded health labels collapse continuous degradation into coarse categories, which can hide useful structure. Second, the adaptive model may learn to use depth as a confidence proxy in a way that is useful for this benchmark but not necessarily optimal under a different operating regime. Those limitations belong in the final discussion so the paper remains credible rather than purely promotional.
