\section{Implementation}
\subsection{Windowing and Labeling}
The training pipeline converts each asset trajectory into overlapping windows with a fixed history length and stride. For the primary C-MAPSS FD001 experiment, windows use length 32 and stride 8. Each window receives the class label associated with its final timestep, where RUL thresholding maps engine state to normal, warning, and critical categories. The same endpoint also drives a derived maintenance-action label, while a coarse subsystem label is assigned from grouped sensor drift. For IMS, label construction is derived from run ordering and normalized progress-to-failure rather than shipped supervision, and the implementation caches summary-statistic features to keep repeated exploratory runs tractable. Stage-aware temporal validation splits reserve the tail of each health stage so validation includes normal, warning, and critical windows.

\subsection{Model Variants}
Three model families are implemented in the codebase. The first is a direct GRU-based baseline that maps each telemetry window to a class prediction in one pass. The second is a fixed-depth recurrent model that repeats the same latent transformation for six steps. The third is the adaptive model, which reuses the same latent block but exits once the classifier confidence crosses a threshold of 0.8. All three variants now emit three heads from the final latent state: health class, maintenance action, and subsystem attribution.

\subsection{Training Recipe}
All primary runs use AdamW with learning rate $10^{-3}$, weight decay $10^{-4}$, hidden size 128, batch size 128, and six training epochs. The code standardizes features using training-set statistics and stores those normalization parameters with each checkpoint. Validation splits are created at the asset level for C-MAPSS so that windows from the same engine do not appear in both training and validation sets. No class weighting or data augmentation was used in the current results, which makes the adaptive-compute comparison easier to interpret.

\subsection{Evaluation Pipeline}
Evaluation runs on a held-out test set with frozen thresholds. For the adaptive model, every example emits both a class prediction and a depth statistic so that correctness and compute use can be analyzed together. The code writes metric summaries, confusion matrices, task-specific reports for health, action, and subsystem heads, latency benchmarks, and training-history CSV files to an artifact directory for each run.

\begin{algorithm}[t]
\caption{Adaptive looped maintenance inference}
\label{alg:adaptive}
\begin{algorithmic}[1]
\STATE Encode input window into latent state $h_0$
\FOR{$k = 0$ to $K-1$}
    \STATE Update latent state $h_{k+1} \leftarrow f_\theta(h_k, c)$
    \STATE Compute class confidence $p_{\text{exit}}^{(k)}$
    \IF{$p_{\text{exit}}^{(k)}$ exceeds threshold}
        \STATE Break and emit final prediction
    \ENDIF
\ENDFOR
\STATE Apply task heads to final latent state
\end{algorithmic}
\end{algorithm}
