\section{Introduction}
\subsection{Problem Statement}
Predictive maintenance systems aim to detect degradation early enough to reduce downtime, avoid secondary damage, and schedule service before failure. In practice, the core challenge is not just classification accuracy, but making good decisions under limited compute, noisy telemetry, and incomplete operational context. Benchmark datasets such as C-MAPSS have made this problem concrete for RUL-style forecasting, but they also expose the limits of one-pass prediction when failure evidence accumulates gradually \cite{Saxena2008CMAPSS,Ramasso2014CMAPSS}.

That setting matches the strengths of looped latent reasoning: the model can refine an internal state iteratively and stop early when the evidence is already clear. Methods such as adaptive computation time and recurrent latent refinement show that depth itself can be a learned resource rather than a fixed architectural constant \cite{Graves2016ACT,Dehghani2018UniversalTransformers,Zhu2025Ouro}.

This work studies whether an adaptive looped architecture can improve maintenance triage on sequential industrial sensor data across multiple equipment domains. The central hypothesis is that recurrent latent computation with learned depth allocation will produce better calibration and compute-efficiency tradeoffs than fixed-depth baselines on difficult failure windows, while remaining competitive on easier cases. The evaluation therefore spans engine telemetry, run-to-failure bearing vibration, machinery state monitoring, and HVAC fault trajectories rather than relying on a single benchmark family \cite{NASAIMSBearings}.

The paper makes three contributions. First, it defines a predictive-maintenance formulation that maps sensor windows to health state, urgency, and recommended action. Second, it proposes an Ouro-inspired model with shared iterative computation and early exit. Third, it establishes an evaluation protocol spanning classification quality, compute use, and maintenance utility.

\subsection{Why It Matters}
For this project, the central research question is whether a looped transformer-style latent reasoning system can outperform a pretrained LLM baseline on maintenance triage while using less inference compute. That comparison matters because many current AI workflows default to generic language-model pipelines even when the underlying data are numeric sensor streams.

\subsection{Contributions}
\begin{itemize}
    \item A maintenance-oriented reformulation of looped reasoning for health monitoring and triage.
    \item A reproducible architecture that separates window encoding, latent recurrence, and adaptive exit.
    \item A completed benchmark suite spanning C-MAPSS, IMS, Paderborn, and LBNL HVAC data, with looped-model comparisons against task-specific LLM baselines wherever matched runs completed under the same protocol.
\end{itemize}

\subsection{Scope}
The report is organized as a benchmark matrix rather than a single-dataset case study. C-MAPSS FD001 serves as the deepest comparison because it includes direct, fixed-depth, adaptive, frozen-LLM, and task-adapted-LLM baselines on an official test split. FD002--FD004, three IMS runs, and the reduced Paderborn benchmark test whether the adaptive-versus-LLM ordering persists across additional datasets. The reduced LBNL HVAC benchmark is reported as a transfer study for the looped model because matched HVAC LLM runs were not practical on the available laptop CPU.
